\documentclass[../final.tex]{subfiles}
%Make sure to start with subsubsection for sectioning
The database is organized around the core elements of camps, surveys, and responders.
These will compromise the three core tables in the database, with other tables existing for administrators, frequently used questions, reports, and responses.
All tables contain unique IDs (or combinations of IDs from other tables) as their primary key, and each ID is a non-negative integer.

The Camp table contains a \emph{camp\_id}, the \emph{title} of the Camp, and each Camp's \emph{start\_date} and \emph{end\_date}.
A Camp entry also has a \emph{pre} and a \emph{post} attribute, which are integers that connect to the pre-camp and post-camp survey IDs, respectively.
Lastly, an \emph{enrollment} attribute stores a string respresentation of the students enrolled in the camp.

The Survey table contains the \emph{survey\_id} as its primary key to identify each individual Survey.
Each Survey will also contain a \emph{title}, a string representing the questions in the survey called \emph{arr\_questions}, and the type of survey stored as \emph{survey\_type} (i.e. is it a pre- or post-camp survey?).

The Responder table will store information on the individual students taking surveys.
This includes a unique \emph{responder\_id} for the primary key, a student's \emph{first\_name} and \emph{last\_name}, their \emph{birthdate}, and their \emph{age}.
Additional demographic information is also stored for each student: their \emph{gender}, \emph{race}, \emph{ethnicity}, their free or reduced \emph{lunch\_status}, and the \emph{highest\_education} level their parent(s) or guardian(s) received.

The Admin table contains information for administrative users to login to the website.
This information consists of a unqiue \emph{admin\_id}, their \emph{first\_name} and \emph{last\_name}, and their \emph{user\_name} and \emph{password}.

The Question table stores frequently used questions.
It stores a \emph{question\_id} (separate from the \emph{Q\_id} used in JSON representations of surveys and questions), the \emph{type} of the question (i.e. "text" or "matrix"), and the \emph{obj\_string} which stores a question's JSON representation as a string.

The Report able is used for saving reports STEM Academy might reuse.
Reports are stored with a \emph{report\_id}, a \emph{title}, and the results JSON object stored as a string in \emph{arr\_results}.

Lastly, the Response table stores individuals' responses to surveys.
This is stored wtih a \emph{camp\_id}, \emph{responder\_id}, and a \emph{survey\_id} to reference the associated camp, survey, and student, their JSON object for their \emph{answers} represented as a string, and the \emph{survey\_type}.
\subsubsection{Demographic Information}
Demographic information is updated in the database when students take their surveys.
Based on specific question IDs (tied to the demographic survey questions), responses to those questions are stored in the appropriate field in the Responder's entry.