\documentclass[../final.tex]{subfiles}

\begin{document}
\subsubsection{Javier Franco: Report Generation}
The technical information that I learned by working on this project is that I learned how to create a JSON object in JavaScript to send to PHP to store in a database table. This helps reduced the number of tables that are needed for storing information. Another thing that I learned in this project is the that it is important to have an onload function in HTML web page to populate the first dropdown menu to prevent a delay in the other dropdown menus when they are populated. Furthermore, I learned how to generate an HTML object using a JSON object. I also learned the process of sending a variable between JavaScript and PHP using an XMLHTTP request which was something that I did not know how to do very well. 

 What I have learned working in a team is that having a group leader is important because they setup meetings to check on the current progress of each person in the group and they also address the things that need to be finished before a deadline. If a group did not have a group leader I feel that the group will be less focused on finishing the project and it would also result in less group meetings. I learned debugging as a team is very effective because certain members in a group can identify bugs that are causing a problem more quickly due to their experience which saves time. Another thing that I learned is that it is important to communicate with your team members if you do not understand something, so that they can help you. I learned that if a group member has less work to do it is very helpful to the group when they work on other parts of the project or help out other group members with their parts in order to make more progress. I learned that writing clean code is very important, so that other group members are able to help you with your part. This is something that I am going to work on because I was coding on the fly instead of thinking things through and writing out a plan.
 
 If could do this project all over again I would have asked the clients to be more specific of the requirements they requested for the report generation page. The reason why I say this is because I was returning a single value based on a response that was selected for a multiple choice question, but this is not what they wanted instead they wanted a table that broke down the result of each response. I found this out during the 2nd to last week of Spring term and I had to change the result that is returned for a multiple choice question. I also had to write code for returning the results of a student's survey which I felt was not in the requirements document due to the requirements not being specific enough.
 Another thing that I would have changed is that I would have used my Winter and Spring breaks more effectively to make more progress on the project and to get feedback from the clients which would have reduced significantly the amount of work I had to do Spring term. Furthermore, I would have practiced using AngularJS because many of my friends recommended using it for our project. For presenting at expo I would have practiced my pitch and come up with responses to potential questions this would have made me more confident talking to people at expo. 
\end{document}